---
title: "DSTrack_PracticalMLAssignment"
output: html_document
---
Prediction Assignment
=============================

```{r output='hide'}
options(warn=-1)
library(caret)
library(randomForest)
library(Hmisc)

library(foreach)
library(doParallel)
set.seed(4356)
```

The first step is to load the csv file data to dataframe:

```{r}
data <- read.csv("C:/Users/DELL/Desktop/D.Science/8.predmachlearn-002/pml-training.csv")
#summary(data)
#describe(data)
#sapply(data, class)
#str(data)
```


```{r}
data <- read.csv("C:/Users/DELL/Desktop/D.Science/8.predmachlearn-002/pml-training.csv", na.strings=c("#DIV/0!") )
data_cv <- read.csv("C:/Users/DELL/Desktop/D.Science/8.predmachlearn-002/pml-testing.csv" )
```

And force the cast to numeric values for the specified columns (i.e.: 8 to end) :

```{r}
#cData <- rbind(data[,1:159],data_cv[,1:159])
cData <- data#[,1:159]
for(i in c(8:ncol(cData)-1)) {cData[,i] = as.numeric(as.character(cData[,i]))}
tData <- data_cv
for(i in c(8:ncol(tData)-1)) {tData[,i] = as.numeric(as.character(tData[,i]))}
```


```{r}
featuresnames <- colnames(cData[colSums(is.na(cData)) == 0])[-(1:7)]
features <- cData[featuresnames]
tData$classe <- 1
tData <- tData[featuresnames]
```

We have now a dataframe "features which contains all the workable features. So the first step is to split the dataset in two part : the first for training and the second for testing.

```{r}
xdata <- createDataPartition(y=features$classe, p=.9, list=FALSE )
training <- features[xdata,]
testing <- features[-xdata,]
```


```{r}
registerDoParallel()
model <- foreach(ntree=rep(100, 4), .combine=randomForest::combine) %dopar% randomForest::randomForest(training[-ncol(training)], training$classe, ntree=ntree)
```

To evaluate the model we will use the confusionmatrix method and we will focus on accuracy, sensitivity & specificity metrics :

```{r}
predictionsTr <- predict(model, newdata=training)
confusionMatrix(predictionsTr,training$classe)

predictionsTe <- predict(model, newdata=testing)
confusionMatrix(predictionsTe,testing$classe)

```


```{r}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("C:/Users/DELL/Desktop/D.Science/8.predmachlearn-002/problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
answers = predictionsFinal <- predict(model, newdata=tData)
pml_write_files(answers)
```
